Supplementary Appendix

### 2023-06-23 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd

---
output:
  html_document: default
---
# Reply to the editor

@@

Blur blur, . Your comments are in blue, and our responses are in black.

<span style = "color: blue;"> Based on the reviews and your email response, I have decided to give you the opportunity to revise the manuscript and respond to reviewer comments. One major point is that your true DGP assumed a quadratic plateau, but the estimated models use quadratic. This will lead the estimated models to give biased results. In your email response you indicate that you used quadratic plateau as the “true” functional form based on agronomy studies. If the dominant approach in recent literature is to use quadratic functions, then it does seem valuable to quantify the bias from using quadratic rather than quadratic plateau. Please document clearly in the manuscript that quadratic is the common practice (__point 1__). However, the title of your paper is about an economic evaluation of GWR analysis, and the choice of quadratic or quadratic-plateau is not an issue with GWR and this needs to be clear (__point 2__). Also reading through your discussion section, the implications are primarily framed about how GWR performed, but it might completely be an issue with functional form, but the current simulations don't inform us about the source of bias. Ideally, you would compare a GWR model that is quadratic with a GWR model that is quadratic-plateau functional form (__point 3__). </span>

Reply to <span style = "color: blue;"> __point 1__ </span>:

Actually, the dominant functional form used in the literature is quadratic-plateau for <span style = "color: red;"> non-</span>GWR (regualr parametric) regression because agronomists have long known that it better represents corn-nitrogen relationship. Application of GWR is very new to the field and GWR is not currently flexible in funcional form. There is no readily available statistical software or packages that lets researchers use the quadratic-plateau functionl form under the GWR framework. That is the primary reason that both Trevisan et al () and Rakshit et al () are using quadratic functional form. So, their choice of functional form is not coming from agronomic facts, rather from technical limitations. We are trying to point out this can be dangerous with GWR just like it is a problem for regular regression framework. So, our paper is imporatnt because many use quadratic-plateau in regular regression framework for corn-nitrogen yield response function estimation, but the GWR promoted by the two studies use quadratic just because it is hard to do so. We believe that this technical limitation is not trivial and would like to avoid practitioners or researcher believing GWR is better than it truly is. We further suggest that it is important to develope a statistical package that allows to model yield-input relationship more flexibly.

@@

<span style = "color: blue;"> The other major critique of reviewer #1 is that the “true” DGP of the parameters does not correspond with a GWR. For example, reviewer #1 argues that the spatial distribution of parameters described in lines 173-193 does not correspond with a GWR DGP. Is there evidence from the agronomy literature that the DGP (aside from the functional form assumption) follows the process that you specify? Or alternatively, is there evidence from the agronomy literature that the DGP does not follow the GWR DGP described by reviewer #1 in comment #5? My guess is that the agronomy literature has little or nothing to say about this (compared to the functional form assumption), but maybe I'm wrong about that. If there is no evidence to support your proposed DGP or the GWR DGP as “true,” then it is difficult to critique GWR for not correctly estimating your proposed DGP (__specific point 1__). In your email response you state “Our choice of true yield response function is deliberate and just as valid as the data generating process Reviewer #1 recommends.” But if the DGP that you used and the DGP recommended by reviewer #1 are equally valid, then why critique GWR for not correctly estimating your DGP? To critique GWR, you need to argue that your DGP is more valid than the GWR DGP (__specific point 2__). Or you can estimate if GWR is robust to alternative, but equally valid, DGPs.

</span>

First, it is important to reiterate that we are not interested in evaluating GWR itself even though our writing did give that impression, rather we are interested in evaluating GWR with quadratic functional form when the true underlying relationship is quadratic-plateau. This point alone addresses lots of your and reviwer 1's comments (as we discussed above, this is an important problem to address). We are critiqing the use of GWR with quadratic functional form when the true underlying relationship is quadratic-plateau.

@@

Another way of writing this is simply

$$
\begin{aligned}
y_i = X_i\beta_i + e_i
\end{aligned}
$$

as shown in Leung, Y., Mei, C. L., & Zhang, W. X. (2000), where $\beta_i$ is the coefficient specific to observation $i$. $W(s)$ ensures that $\beta$ are spatially correlated. The choice of $W(s)$ is arbitrary and if you use the same $W(s)$ used in DGP for GWR regression as well, then you would be cheating, giving an unfair advantage to GWR because we (researchers) never know $W(s)$ in reality just like we do not know the weight matrix in spatial econometric approaches like spatial error model. This is the "correct" GWR DGP only if you know what $W(s)$ is priori.

In our DGP, we generate parameters (alpha, ... in equation )for individual $i$ in a spatially correlated manner (as opposed to what the reviewer 1 thought). So, aside from the functional form, the only difference is in the spatial pattern of parameters. It is kind of like, we are using a different $W(s)$ in the above equation, which is an arbitrary parameter chosen by the researcher running MC simulations in the first place. In this sense, our DGP is just as "valid" as the GWR DGP.

### 2023-06-23 Writing/supplementary_appendix.rmd

```{r}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(ggplot2)
```

```{r figure_setup}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, family = "Times"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

```{r include = FALSE}
kernel_ls <- c("gaussian", "exponential", "boxcar", "bisquare", "tricube")

gg_appendix <-
  data.frame(kernel = kernel_ls) %>%
  rowwise() %>%
  mutate(results = list(
    here("Shared", "Results", kernel, "pi_data.rds") %>%
      readRDS() %>%
      .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
      .[, bias := pi_diff_est - pi_diff] %>%
      # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
      .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
      # === label price ratio
      .[, pLabelName := "Price Ratio (N/corn)"] %>%
      .[pRatio == 5.44, pLabel := "Low"] %>%
      .[pRatio == 6.56, pLabel := "Middle"] %>%
      .[pRatio == 7.67, pLabel := "High"] %>%
      .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
  )) %>%
  #* ===========================================================
  #* Plots of the value of GWR
  #* ===========================================================
  mutate(median_data_value = list(
    results %>%
      .[, .(pi_diff = median(pi_diff)),
        by = c("field_col", "pLabel", "type")
      ]
  )) %>%
  mutate(g_value = list(
    results %>%
      ggplot(data = .) +
      geom_histogram(
        aes(x = pi_diff),
        fill = NA,
        color = "blue",
        bins = 50,
        size = 0.2
      ) +
      geom_vline(
        data = median_data_value,
        aes(xintercept = pi_diff),
        color = "red",
        size = 0.5
      ) +
      geom_text(
        data = median_data_value, color = "red",
        aes(
          x = ifelse(pi_diff < 65, pi_diff + 5, pi_diff - 20),
          y = 150,
          label = paste0("Median = ", round(pi_diff, 2))
        ),
        angle = 0, hjust = -0.1, vjust = 0, size = 3
      ) +
      facet_grid(pLabel ~ type) +
      scale_y_continuous(expand = c(0, 0), limits = c(NA, 200)) +
      scale_x_continuous(breaks = 20 * (-2:3), limits = c(-45, 60)) +
      xlab("The value of VRA over URA ($ per ha)") +
      ylab("Number of Simulation Cases")
  )) %>%
  #* ===========================================================
  #* Plots of the bias in the value of GWR
  #* ===========================================================
  mutate(median_bias_data = list(
    results %>%
      .[, bias := pi_diff_est - pi_diff] %>%
      .[, .(bias = median(bias)),
        by = c("field_col", "pLabel", "type")
      ]
  )) %>%
  mutate(g_bias = list(
    results %>%
      .[, bias := pi_diff_est - pi_diff] %>%
      .[bias < 150, ] %>%
      ggplot(data = .) +
      geom_histogram(
        aes(x = bias),
        fill = NA,
        color = "blue",
        size = 0.2,
        bins = 50
      ) +
      geom_vline(
        data = median_bias_data, aes(xintercept = bias),
        color = "red",
        size = 0.5
      ) +
      geom_text(
        data = median_bias_data, color = "red",
        aes(
          x = ifelse(bias < 65, bias + 2, bias - 85), y = 100,
          label = paste0("Median = ", round(bias, 2))
        ),
        angle = 0, hjust = -0.1, vjust = 0, size = 3
      ) +
      facet_grid(pLabel ~ type) +
      scale_y_continuous(expand = c(0, 0)) +
      xlab("Bias in the Estimation of the Value of VRA over URA ($ per ha)") +
      ylab("Number of Simulation Cases")
  )) %>%
  select(kernel, g_value, g_bias)
```

@@

@@

```{r, fig.id = "price", fig.cap = "Historical monthly variations in corn price, nitrogen fertilizer price, and the corresponding nitrogen-corn price ratio, 2002-2022"}
knitr::include_graphics("price_ratio_history.png")
```

@@

```{r, fig.id = "value-kernel-exp", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Exponential kernel function", fig.height = 3.5}
gg_appendix$g_value[[2]]
```

```{r, fig.id = "value-kernel-boxcar", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Boxcar kernel function", fig.height = 3.5}
gg_appendix$g_value[[3]]
```

```{r, fig.id = "value-kernel-bs", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Bi-square kernel function", fig.height = 3.5}
gg_appendix$g_value[[4]]
```

```{r, fig.id = "value-kernel-tricube", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Tri-cube kernel function", fig.height = 3.5}
gg_appendix$g_value[[5]]
```

@@

```{r, fig.id = "bias-kernel-exp", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Exponential kernel function", fig.height = 3.5}
gg_appendix$g_bias[[2]]
```

```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Boxcar kernel function", fig.height = 3.5}
gg_appendix$g_value[[3]]
```

```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Bi-square kernel function", fig.height = 3.5}
gg_appendix$g_value[[4]]
```

```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Tri-cube kernel function", fig.height = 3.5}
gg_appendix$g_value[[5]]
```

>>>>

```{r}
#--- packages ---#
library(data.table)
library(tidyverse)
library(patchwork)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(ggplot2)
```

```{r figure_setup}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, family = "Times"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 9, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.title =
    element_text(
      size = 9, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10, family = "Times"),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

```{r results-plots, include = FALSE}
kernel_ls <- c("gaussian", "exponential", "boxcar", "bisquare", "tricube")

gg_appendix <-
  data.frame(kernel = kernel_ls) %>%
  rowwise() %>%
  mutate(results = list(
    here("Shared/Results", kernel, "pi_data.rds") %>%
      readRDS() %>%
      .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
      .[, bias := pi_diff_est - pi_diff] %>%
      # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
      .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
      # === label price ratio
      .[, pLabelName := "Price Ratio (N/corn)"] %>%
      .[pRatio == 5.44, pLabel := "Low"] %>%
      .[pRatio == 6.56, pLabel := "Middle"] %>%
      .[pRatio == 7.67, pLabel := "High"] %>%
      .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))] %>%
      .[, p_ratio_text := paste0("Price Ratio (N/Corn) \n = ", pRatio, " (", pLabel, ")")]
  )) %>%
  #* ===========================================================
  #* Plots of the value of GWR
  #* ===========================================================
  mutate(median_data_value = list(
    results %>%
      .[, .(pi_diff = median(pi_diff)),
        by = .(field_col, p_ratio_text, type)
      ]
  )) %>%
  mutate(g_value = list(
    results %>%
      ggplot(data = .) +
      geom_histogram(
        aes(x = pi_diff),
        fill = NA,
        color = "blue",
        bins = 50,
        size = 0.2
      ) +
      geom_vline(
        data = median_data_value,
        aes(xintercept = pi_diff),
        color = "red",
        size = 0.5
      ) +
      geom_text(
        data = median_data_value, color = "red",
        aes(
          x = ifelse(pi_diff < 65, pi_diff + 5, pi_diff - 20),
          y = 150,
          label = paste0("Median = ", round(pi_diff, 2))
        ),
        angle = 0, hjust = -0.1, vjust = 0, size = 3,
        family = "Times"
      ) +
      facet_grid(p_ratio_text ~ type) +
      scale_y_continuous(expand = c(0, 0), limits = c(NA, 200)) +
      scale_x_continuous(breaks = 20 * (-2:4), limits = c(-45, 80)) +
      theme(
        panel.spacing.y = unit(0.3, "cm")
      ) +
      xlab("The value of VRA over URA ($ per ha)") +
      ylab("Number of Simulation Cases")
  )) %>%
  #* ===========================================================
  #* Plots of the bias in the value of GWR
  #* ===========================================================
  mutate(median_bias_data = list(
    results %>%
      .[, bias := pi_diff_est - pi_diff] %>%
      .[, .(bias = median(bias)),
        by = .(field_col, p_ratio_text, type)
      ]
  )) %>%
  mutate(g_bias = list(
    results %>%
      .[, bias := pi_diff_est - pi_diff] %>%
      .[bias < 150, ] %>%
      ggplot(data = .) +
      geom_histogram(
        aes(x = bias),
        fill = NA,
        color = "blue",
        size = 0.2,
        bins = 50
      ) +
      geom_vline(
        data = median_bias_data, aes(xintercept = bias),
        color = "red",
        size = 0.5
      ) +
      geom_text(
        data = median_bias_data, color = "red",
        aes(
          x = ifelse(bias < 65, bias + 2, bias - 85), y = 100,
          label = paste0("Median = ", round(bias, 2))
        ),
        angle = 0, hjust = -0.1, vjust = 0, size = 3,
        family = "Times"
      ) +
      facet_grid(p_ratio_text ~ type) +
      scale_y_continuous(expand = c(0, 0)) +
      theme(
        panel.spacing.y = unit(0.3, "cm")
      ) +
      xlab("Bias in the Estimation of the Value of VRA over URA ($ per ha)") +
      ylab("Number of Simulation Cases")
  )) %>%
  select(kernel, g_value, g_bias)
```

@@

```{r price-history-plot, include = FALSE}
# read the data
price_ratio_data <- readRDS(here("Shared/Data/price_ratio_data.rds"))

# continuous time variable
price_ratio_data[, Time := Year + Month / 12]

# color legend
color_legend <- c("Corn" = "black")

# corn price
g1 <-
  ggplot(data = price_ratio_data) +
  geom_line(aes(x = Time, y = pCorn), color = "black", linewidth = 0.6) +
  ggtitle("Corn price ($/kg)") +
  ylab("") +
  xlab("Year") +
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, vjust = -1, size = 9),
    axis.text = element_text(color = "black"),
    axis.title.x = element_text(hjust = 1)
  )

# N price
g2 <-
  ggplot(data = price_ratio_data) +
  geom_line(
    aes(x = Time, y = pN, color = Ntype, linetype = Ntype),
    linewidth = 0.6
  ) +
  scale_color_brewer(palette = "Dark2") +
  ggtitle("Nitrogen price ($/kg)") +
  ylab("") +
  xlab("Year") +
  labs(color = "Nitrogen type", linetype = "Nitrogen type") +
  theme(
    plot.title = element_text(hjust = 0.5, vjust = -1, size = 9),
    axis.text = element_text(color = "black"),
    axis.title.x = element_text(hjust = 1),
    legend.key.width = unit(1, "cm")
  )

# price ratio
g3 <-
  ggplot(data = price_ratio_data) +
  geom_line(
    aes(x = Time, y = pRatio, color = Ntype, linetype = Ntype),
    linewidth = 0.6
  ) +
  scale_color_brewer(palette = "Dark2") +
  ggtitle("Nitrogen-Corn price ratio") +
  ylab("") +
  xlab("Year") +
  labs(color = "Nitrogen type", linetype = "Nitrogen type") +
  theme(
    plot.title = element_text(hjust = 0.5, vjust = -1, size = 9),
    axis.text = element_text(color = "black"),
    axis.title.x = element_text(hjust = 1),
    legend.key.width = unit(1, "cm")
  )

g_prices <- g1 / g2 / g3
```

@@

```{r, fig.id = "price", fig.cap = "Historical monthly variations in corn price, nitrogen fertilizer price, and the corresponding nitrogen-corn price ratio, 2002-2022", fig.width = 6, fig.height = 6}
g_prices
```

@@

```{r, fig.id = "value-kernel-exp", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Exponential kernel function", fig.height = 6}
gg_appendix$g_value[[2]]
```

```{r, fig.id = "value-kernel-boxcar", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Boxcar kernel function", fig.height = 6}
gg_appendix$g_value[[3]]
```

```{r, fig.id = "value-kernel-bs", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Bi-square kernel function", fig.height = 6}
gg_appendix$g_value[[4]]
```

```{r, fig.id = "value-kernel-tricube", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Tri-cube kernel function", fig.height = 6}
gg_appendix$g_value[[5]]
```

`r run_pagebreak()`

@@

```{r, fig.id = "bias-kernel-exp", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Exponential kernel function", fig.height = 6}
gg_appendix$g_bias[[2]]
```

```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Boxcar kernel function", fig.height = 6}
gg_appendix$g_value[[3]]
```

```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Bi-square kernel function", fig.height = 6}
gg_appendix$g_value[[4]]
```

```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Tri-cube kernel function", fig.height = 6}
gg_appendix$g_value[[5]]
```

`r run_pagebreak()`

# References

<br />

<div id="refs"></div>
